---
title: "InDetail3-ConceptNetworkOverview"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{InDetail3-ConceptNetworkOverview}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.width = 6, fig.height = 6
)
```

## Introduction
This tutorial guides you through creation of a concept network plot. A concept network is a way to visualise words which often occur together.

Our concept network function uses the TextRank algorithm which is a graph-based ranking model for text processing. Vertices represent words and co-occurrence between words is shown through edges. Word importance is determined recursively (through the unsupervised learning TextRank algorithm) where words get more weight based on how many words co-occur and the weight of these co-occurring words. 

To utilise the TextRank algorithm in `finnsurveytext`, we use the `textrank` package. For further information on the package, please see [this documentation](https://cran.r-project.org/web/packages/textrank/vignettes/textrank.html). This package implements the TextRank and PageRank algorithms. (PageRank is the algorithm that Google uses to rank webpages.) You can read about the underlying TextRank algorithm [here](https://web.eecs.umich.edu/~mihalcea/papers/mihalcea.emnlp04.pdf) and about the PageRank algorithm [here](https://www.sciencedirect.com/science/article/abs/pii/S016975529800110X).  

### Installation of package.

Once the package is installed, you can load the `finnsurveytext` package as below:
(Other required packages such as `dplyr` and `stringr` will also be installed if they are not currently installed in your environment.)

```{r setup}
library(finnsurveytext)
```

### Overview of Functions 
The functions covered in this tutorial are in r/03_concept_network.R. These are: 

1. `fst_cn_search()`
2. `fst_cn_edges()`
3. `fst_cn_nodes()`
4. `fst_cn_plot()`
5. `fst_concept_network()`

### Data 

There are two sets of data files available within the package which could be used in this tutorial. These files have been created following the process demonstrated in Tutorial 1. The suffixes 'iso', 'nltk' and 'snow' refer to the types of stopwords which have been removed during the data preparation activities.  

#### 1. Child Barometer Data
* data/fst_child

#### 2. Development Cooperation Data
* data/fst_dev_coop

You can read these in as follows: 

```{r}
df1 <- fst_child
df2 <- fst_dev_coop
```

## FUNCTIONS

### Concept Network - Search TextRank for Concepts
`fst_cn_search()`

This function is used to find words which are related to a list of provided terms. It utilises the `textrank_keywords()` function which is part of the `textrank` package.

This function goes through the following process: 

1. separates the search string into individual terms
2. applies the `textrank_keywords()` function which finds n-grams in the text that occur multiple times
3. finds all pairs of words included in these common ngrams 
4. filters the pairs so that at least one of the pair is a searched term. 

The function `fst_cn_search()` is demonstrated below.
```{r}
bullying_concepts <- fst_cn_search(
  data = df1,
  concepts = "kiusata, lyöminen, lyödä, potkia"
)
dev_concepts <- fst_cn_search(
  data = df2,
  concepts = "köyhyys, nälänhätä, sota, ilmastonmuutos, puute"
)
```

The resulting dataframe is formatted as below:
```{r}
knitr::kable(head(dev_concepts, n = 10))
```

To run `fst_cn_search`, we provide the following arguments to the function:

1. `data` which is output from data preparation, prepared data in CoNLL-U format, such as the output of `fst_prepare_connlu()`. 
2. `concepts` is a string of concept terms to search for, separated by commas.
3. `relevant_pos` is a list of UPOS tags for inclusion, default is c("NOUN", "VERB", "ADJ", "ADV").

### Concept Network - Get TextRank Edges
`fst_cn_edges()`

The Get Edges function runs the search function, `fst_cn_search()` and then filters for edges (pairs of co-occurring words where one is a concept word) which are larger than the threshold (occurring enough times). The resulting dataframe is simplified in preparation for plotting.

```{r}
bullying_edges <- fst_cn_edges(
  data = df1,
  concepts = "kiusata, lyöminen, lyödä, potkia"
)

dev_edges <- fst_cn_edges(
  data = df2,
  concepts = "köyhyys, nälänhätä, sota, ilmastonmuutos, puute",
  threshold = 2
)
```

The dataframe has a simplified format from the `fst_cn_search()` results, with only columns "to", "from" and "n" which indicates the number of occurrences.

```{r}
knitr::kable(head(dev_edges, n = 10))
```

The arguments are the same as for `fst_cn_search()` plus the `threshold`.

1. `data` which is output from data preparation, prepared data in CoNLL-U format, such as the output of `fst_prepare_connlu()`.
2. `concepts` is a string of concept terms to search for, separated by commas.
3. `threshold` is the minimum number of occurrences threshold for 'edge' between a concept term and other word, default is NULL.
4. `norm` is the method for normalising the data. Valid settings are `'number_words'` (the number of words in the responses, default), `'number_resp'` (the number of responses), or `NULL` (raw count returned). Normalisation occurs **after** the threshold (if it exists) is applied. 
5. `pos_filter` is a list of UPOS tags for inclusion, default is `NULL`.

### Concept Network - Get TextRank Nodes
`fst_cn_nodes()`

This function runs the `textrank_keywords()` function which is part of the `textrank` package and returns a dataframe containing relevant lemmas and their associated PageRank. 

It is demonstrated as follows:
```{r}
bullying_nodes <- fst_cn_nodes(data = df1, edges = bullying_edges)
dev_nodes <- fst_cn_nodes(data = df2, edges = dev_edges)
```

```{r}
knitr::kable(head(dev_nodes, n = 10))
```

`fst_cn_nodes()` requires the following arguments:

1. `data` which is output from data preparation, prepared data in CoNLL-U format, such as the output of `fst_prepare_connlu()`.
2. `edges` is the output from `fst_cn_edges()`.
3. `pos_filter` is a list of UPOS tags for inclusion, default is `NULL`.

### Plot Concept Network
`fst_cn_plot()`

This function takes the output of the previous functions and plots the concept network. Edges between words in the plot show the number of occurrences with thicker and more opaque edges showing more occurrences. Similarly, the size of the word circle indicates the PageRank with higher PageRank resulting in a larger circle. Concept words are coloured red and other terms are black.

```{r}
fst_cn_plot(
  edges = bullying_edges,
  nodes = bullying_nodes,
  concepts = "kiusata, lyöminen",
  title = "Bullying Data CN"
)
```


Recall that for `dev_edges` we have set the `threshold` as 2. This is why there are fewer words included in the plot despite more words available (including stopwords) in this data.
```{r}
fst_cn_plot(
  edges = dev_edges,
  nodes = dev_nodes,
  concepts = "köyhyys, nälänhätä, sota, ilmastonmuutos, puute"
)
```

As `fst_cn_plot()` uses results from the previous functions, it has 4 arguments:

1. `edges` is the output of `fst_cn_edges()`.
2. `nodes` is the output of `fst_cn_nodes()`
3. `concepts` is a list of terms which have been searched for, separated by commas.
4. `title` is an optional title for plot, default is `NULL` and a generic title, ('TextRank extracted keyword occurrences') will be used.

### Plot Concept Network
`fst_concept_network()`

If you don't want to run all of the individual functions, `fst_cn_search()`, `fst_cn_edges()`, `fst_cn_nodes()`, and `fst_cn_plot()`, you can run them all within the one function, `fst_concept_network()`.

This function is run as follows:
```{r}
fst_concept_network(
  data = df1,
  concepts = "kiusata, lyöminen",
  title = "Concept Network of Bullying Data"
)
fst_concept_network(
  data = df2,
  concepts = "köyhyys, nälänhätä, sota, ilmastonmuutos, puute"
)
fst_concept_network(
  data = df2,
  concepts = "köyhyys, nälänhätä, sota, ilmastonmuutos, puute",
  threshold = 3
)

```

The arguments are:

1. `data` which is output from data preparation, prepared data in CoNLL-U format, such as the output of `fst_prepare_connlu()`.
2. `concept` is a string of concept terms to search for, separated by commas.
3. `threshold` is the minimum number of occurrences threshold for 'edge' between a concept term and other word, default is NULL.
4. `norm` is the method for normalising the data. Valid settings are `'number_words'` (the number of words in the responses, default), `'number_resp'` (the number of responses), or `NULL` (raw count returned). Normalisation occurs **after** the threshold (if it exists) is applied. 
4. `pos_filter` is a list of UPOS tags for inclusion, default is `NULL`.
5. `title` is an optional title for plot, default is `NULL` and a generic title, ('TextRank extracted keyword occurrences') will be used.

## Conclusion

This tutorial ran you through the functions used to create Concept Networks which are included in `finnsurveytext`. A concept network visualises word importance and co-occurrence between words. 

## Citation

The Office of Ombudsman for Children: Child Barometer 2016 [dataset]. Version 1.0 (2016-12-09). Finnish Social Science Data Archive [distributor]. http://urn.fi/urn:nbn:fi:fsd:T-FSD3134

Finnish Children and Youth Foundation: Young People's Views on Development Cooperation 2012 [dataset]. Version 2.0 (2019-01-22). Finnish Social Science Data Archive [distributor]. http://urn.fi/urn:nbn:fi:fsd:T-FSD2821
