---
title: "InDetail4-ComparisonFunctions"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{InDetail4-ComparisonFunctions}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.width = 8, fig.height = 6
)
```

## Introduction
When analysing responses to open-ended questions, you may want to look into whether different groups of survey participants have, in general, responded differently to the prompt. `finnsurveytext` contains a number of comparison functions which are intended to be used to compare responses between groups. These comparison functions covered are defined in `r/04_comparison_functions.R` and `r/05_comparison_concept_network.R`.

One way to split the data is using a different question within the survey such as a categorical question (eg. gender, location, or level of education) or an ordinal variable (such as age or income bracket). In this tutorial, we will look at comparing responses to a question based on gender. Before using the comparison functions, we run the preparation functions which are in `r/01_prepare_conll-u.R` (and which are covered in detail in 'Tutorial1-Prepare CoNLL-U') for each group separately.  

The comparison functions are: 

1. `fst_summarise_compare()`
2. `fst_pos_compare()`
3. `fst_length_compare()`
4. `fst_comparisoncloud()`
5. `fst_get_unique_ngrams()`
6. `fst_join_unique()`
7. `fst_ngrams_compare_plot()`
8. `fst_ngrams_compare_plot2()`
9. `fst_plot_multiple()`
10. `fst_freq_compare()`
11. `fst_ngrams_compare()`
12. `fst_cn_get_unique()`
13. `fst_cn_compare_plot()`
14. `fst_concept_network_compare()`

We will look at the following question: 

* q11_2  Jatka lausetta: Kehitysyhteistyö on toimintaa, jossa... (Avokysymys)
  + (In English) q11_2 Continue the sentence: Development cooperation is an activity in which... (Open question)

### Installation of package.

Once the package is installed, you can load the `finnsurveytext` package as below:
(Other required packages such as `dplyr` and `stringr` will also be installed if they are not currently installed in your environment.)

```{r setup}
library(finnsurveytext)
```

### The Data

These files have been created following the process demonstrated in Tutorial 1. 

##### 1. Child Barometer Data
* data/fst_child.rda

##### 2. Development Cooperation Data
* data/fst_dev_coop

You can read these in as follows: 

```{r}
df1 <- fst_child
df2 <- fst_dev_coop
```

## Comparison of responses based on gender

All of our comparison functions can compare between groups of respondents based on another field in the raw data which we have included when formatting. The following common arguments appear in multiple functions and are defined the same way in each: 

* `field` is the field in the data used to split the responses. 
* `exclude_nulls` (which has a default value of FALSE) is used to indicate whether we want to include a group of repondents which have no value in the `field` column.
* `rename_nulls` (with default value of 'null_data') is what to name the group with the missing `field` data.

First, we will look at some summary functions to compare the responses overall. 

The functions are: 

1. `fst_summarise_compare()`
2. `fst_pos_summary()`
3. `fst_length_compare()`

#### Make Comparison Summary

We can run this function to create a summary table for our data: 
(we use `knitr::kable` function below to display results in a "prettier" table)
```{r}
knitr::kable(
  fst_summarise_compare(data = df2,
                        field = 'gender',
                        exclude_nulls = FALSE,
                        rename_nulls = 'no gender provided'
  )
)
```

**Remarks:**

We can already see that our data is quite unbalanced. There are a lot more female respondents than male or unspecified. The response (to this question) rate is high (97%) but slightly lower for the unspecified respondents. Unsurprisingly, since there are more female responses, the female responses to this question contain a larger variety of words. 

#### POS and Length Comparisons
Next, we will look at part-of-speech tags and lengths of responses. 

```{r}
knitr::kable(
  fst_pos_compare(data = df2,
                  field = 'gender',
                  exclude_nulls = TRUE
  )
)

knitr::kable(
  fst_length_compare(data = df2,
                     field = 'gender',
                     incl_sentences = TRUE,
                     exclude_nulls = TRUE
  )
)
```


**Remarks:**

In terms of POS tags, the scale differences are likely mostly due to the differences in the number of respondents between genders. We can also see that female responses are generally slightly longer (average of 6 words to 5 words) but that most respondents (across the genders) wrote only a single sentence.

### Comparison Cloud

Now that we've looked at the overview comparisons, we will create a comparison cloud between the responses, using the versions with stopwords removed so that only more meaningful words remain.

A comparison cloud compares the relative frequency with which a term is used in two or more documents. This cloud shows words that occur more regularly in responses from a specific type of respondent. For more information about comparison clouds, you can read [this documentation](https://cran.r-project.org/web/packages/wordcloud/wordcloud.pdf).

We create our comparison cloud as follows: 
```{r}
# WEIGHTED
fst_comparison_cloud(data = df2,
                     field = 'gender',
                     pos_filter = NULL,
                     norm = NULL,
                     max = 100,
                     use_svydesign_weights = FALSE,
                     use_svydesign_field = FALSE,
                     id = "",
                     svydesign = NULL,
                     use_column_weights = TRUE,
                     exclude_nulls = TRUE
)
```

To run `fst_comparison_cloud()`, we provide the following arguments to the function:

* `data`, `field`, `exclude_nulls` and `rename_nulls`` (as defined above)
* `norm` is the method for normalising the data. Valid settings are `'number_words'` (the number of words in the responses), `'number_resp'` (the number of responses), or `NULL` (raw count returned, default).
* `pos_filter` is an optional list of which POS tags to include such as `'c("NOUN", "VERB", "ADJ", "ADV")'`. The default is `NULL`, in which case all words in the data are considered.
* `max` is the maximum number of words to display, the default is `100`. 
* `use_svydesign_weights` is a boolean for whether to get weights for the responses from a `svydesign` object
* If weights are coming from a `svydesign` object, the `id` field needs to not be empty, as this is used to join the data. 
* Similarly, if weights are coming from a `svydesign` object this is the named object.
* `use_column_weights` is a boolean for if weights have already been included in the formatted data and should be included. 

 

### Common Words and N-grams
Now, we will look at common words occurring in the responses. 

First, we will consider all the responses for this question. We are not filtering the data based on POS tag, and will leave the default of `strict = TRUE` which will cut-off the list at 10 words (see the warning note about this). We also use the default for the norm which means we are standardising between groups by dividing count of a word by the total number of words in the responses. 

For definition of `fst_freq_table()` and `fst_ngrams_table()` functions, see "InDetail2-DataExploration". 

```{r}
all_top10 <- fst_freq_table(df2,
  number = 10,
  norm = "number_words",
  pos_filter = NULL,
  strict = FALSE
)
all_top10bigrams <- fst_ngrams_table(df2,
  number = 10,
  ngrams = 2,
  norm = "number_words",
  pos_filter = NULL,
  strict = TRUE
)

knitr::kable(all_top10)
knitr::kable(all_top10bigrams)
```


### Comparison N-Gram Plots 
Now we will look at top words by gender. There are two functions which create the plots in one function simply. These are `fst_freq_compare()` and `fst_ngrams_compare()`. 


```{r}
fst_freq_compare(
  df2,
  field = 'gender',
  number = 10,
  norm = NULL,
  pos_filter = NULL,
  unique_colour = "indianred",
  strict = TRUE, 
  exclude_nulls = TRUE, 
  use_column_weights = TRUE
)

fst_ngrams_compare(
  df2,
  field = 'gender',
  number = 10,
  ngrams = 2,
  norm = NULL,
  pos_filter = NULL,
  unique_colour = "indianred",
  strict = TRUE, 
  use_column_weights = TRUE, 
  exclude_nulls = TRUE
)
```

The functions `fst_freq_compare()` and `fst_ngrams_compare()` have parameters as defined previously.

**Remarks:**
Note that words that are unique to a gender are highlighted in red. This is only comparing the top 10 words, so be aware this word likely still appears in the other genders, just less frequently! Interestingly, while they have the same top 4 words, it seems that the top 3 words differs across the genders with 'ilmastonmuutos' being the 3rd most frequent in male responses but 'nälänhätä' is in the top 3 for females. The most frequent bigram in female responses 'puhdas vesi' is not commonly mentioned by male respondents.

### Comparison Concept Network 
Since the top 4 words are 'köyhyys', 'nälänhätä', 'sota', and 'ilmastonmuutos', we will create Concept Networks based on these terms.

We run the comparison Concept Network as below. Again, we're keeping the default norm. 
```{r}
fst_concept_network_compare(data = df2,
                            concepts = 'köyhyys, nälänhätä, sota, ilmastonmuutos',
                            field = 'gender',
                            norm = NULL,
                            threshold = NULL,
                            pos_filter = NULL,
                            exclude_nulls = TRUE,
                            )
```

The parameters are the same as previously described.

**Remarks:**

Each of these Concept Networks are created separately, which means that the weights of words are based only on the responses within that gender. Despite this, we have many more words in the female plot (possibly due to there being more responses in this data leading to increased variation). 

## Conclusion
As demonstrated in this tutorial, `finnsurveytext` contains a number of functions which can be used to compare responses between groups. This analysis could form the start of further work into the responses to question 11_3 by respondents based on their gender, or as just one of many different splits used to investigate the responses. 

## Citation

Finnish Children and Youth Foundation: Young People's Views on Development Cooperation 2012 [dataset]. Version 2.0 (2019-01-22). Finnish Social Science Data Archive [distributor]. http://urn.fi/urn:nbn:fi:fsd:T-FSD2821
